\documentclass{article}
\usepackage{graphicx} % Required for inserting images

\title{Reading week report}
\author{Daniel Stainer}

\begin{document}
\maketitle
Pick 3 decisions 
For each decision:
Pick an ethical framework to analyze the decision
No need to explain the framework...
Pick decisions such that your framework applies well to some, and not well to others

Decisions:
1. Smith doesn't check through data given to Ben and Sarah by Jess/Takisha, even after Ben and Sarah give him a run-down. He should check  
Chosen because BCS partially applies
Analyse using 10 commandments
2. Feng critiques Ben and Sarah's work, but does it in an uncomfortable way
Chosen because BCS gives a positive image of the situation, although I personally believe Feng should be careful with how he wants to be percieved
Analyse using IEEE code of conduct
3. Ben and Sarah create a big corpus of results  
BCS has a lot to say about this one
Analyse using ACS code of ethics

Introduction
Computer Scientists develop key software upon which many societal functions depend on. As such, it is critical to ensure that inidiviuals in the field act both ethically and professionaly, keeping in mind the best interests of the public, as well as any clients to whom they may be contracted. Ethical frameworks can provide a clear set of criteria by which a reasonable Computer Scientist should act, acting as a concrete ruleset upon which rigourus arguments can be constructed to determine whether a decision is truly Ethical or Unethical. In this report, the ethics of actions carried out by individuals  in a case study/ethics case study/ will be analyzed via selected Ethical frameworks, in order to determine whether said individuals have acted irresponsibly or unethically.                

1.
Upon recieving co-operation from Jess, a PhD student, and Takisha, a post-doctorate graduate, undergraduate 3rd year students Ben and Sarah report back to Smith, their supervisor. Smith's feedback is positive and encouraging. However it could be argued that it  Jess and Takisha have given Sarah and Ben access to their corpi, which they produced in the past, as well as access to a Twitter Academic Research account. However, they have not checked on the Terms and Conditions asserted by Twitter about sharing accounts,  
 
\section*{Introduction}
\end{document}
